---
title: "extra code"
author: "Kathryn Denning"
date: "1/25/2021"
output: html_document
---
## Parent Edu

```{r parent education}
pedu_counts <- clean_ptcheck %>% 
  select(sub_id, parent_education) %>% 
  na.omit() %>% 
  mutate(education = dplyr::recode(parent_education,
                                     `20` = "Less than high school",
                                     `21` = "High school graduate",
                                     `22` = "Some college",
                                     `23` = "Associate's degree",
                                     `24` = "Bachelor's degree",
                                     `26` = "Some graduate school",
                                     `1` = "Master's degree",
                                     `2` = "Doctorate or Professional Degree")) %>% 
  unique() %>% 
  group_by(education) %>% 
  count()

pedu_counts %>% 
  mutate(n_total = sum(edu_counts$n),
    percent = n/n_total*100) %>% 
  select(-n_total)
```

```{r function for plot}
model1_sum$coefficients[[1]]
['selfBFI_c*group_cond']

df <- as.data.frame(mod1_proj_group[1])

separate(df[1])

get_me_group_plot <- function(data, results, groupvar){#for this function, group var must be a two-level categorical var
  group_levs <- levels(data$groupvar)
  group1 <- group_levs[1]
  group2 <- group_levs[2]
  
  mod_effs <- effect(term = "selfBFI_c:group_cond", 
                           xlevels = list(group = c(group1, group2)), 
                           mod = results)

  mod_effs <- as.data.frame(mod_effs)
  return(mod_effs)
}

get_me_group_plot(model1_data, model1_sum, model1_data$group_cond)

group_levs <- list(length(levels(model1_data$group_cond)))
mod_effs <- list()

for (i in seq_along (group_levs)){
  group_levs <- levels(model1_data$group_cond)
  ing <- group_levs[1]
  outg <- group_levs[2]
  
  mod_effs <- effect(term = "selfBFI_c:group_cond", 
                           xlevels = list(group = c(ing, outg)), 
                           mod = model1_sum)
  
  return(mod_effs)
}
  
  
  
  

  mod_effs <- as.data.frame(mod_effs)
  return(mod_effs)
}
```

# Mod 2: Stereo by group BFI only

```{r model 2 data}
model2_data <- clean_ptcheck %>% 
  select(sub_id, BFI_number, BFI_target_group, stereoBFI_c, selfBFI_c, 
         group_cond, opin_pol_combined, TargBFI) %>% 
  na.omit() %>% 
  unique()
```

**Getting effects coding for target group:**

```{r model 2 contrasts}
contrasts(model2_data$group_cond) <- contr.sum(2)
contrasts(model2_data$group_cond)
````

## Using BFI

```{r model 2 BFI results}
model2 <- lmer(TargBFI ~ stereoBFI_c*group_cond + (stereoBFI_c|sub_id),
               data = model2_data)

summary(model2)
```

### Plot: ME target group

```{r}
describe(model2_data$stereoBFI_c)

mod2_plotdata <- effect(term = "stereoBFI_c:group_cond", 
                           xlevels = list(group_cond = c("In-group", 
                                                         "Out-group"),
                                          stereoBFI_c = c(-1.22, 0, 1.22)), 
                           mod = model2)

mod2_plotdata <- as.data.frame(mod2_plotdata)
```

```{r model 2 plot}
ggplot(mod2_plotdata, aes(stereoBFI_c, fit, group = group_cond)) +
  geom_smooth(method = "lm", 
              se = FALSE, 
              size = .7, 
              colour = "black", 
              aes(linetype = group_cond)) +
  theme_minimal() +
  labs(title = "Plot from Model 2: Effect of target group on stereotyping",
       subtitle = "Higher correspondence between BFI ratings indicates more stereotyping",
       y = "BFI ratings for target",
       x = "BFI ratings for stereotypical group member") +
   theme(legend.title = element_blank())
```

People stereotype their in-group more than the out-group on the BFI.

## Using ED

```{r model 2 ED data}
model2ED_data <- clean_ptcheck %>% 
  select(sub_id, ED_number, TargED, stereoED_c, 
         group_cond, opin_pol_combined) %>% 
  na.omit() %>% 
  unique()
```

```{r model 2 ED results}
model2ED <- lmer(TargED ~ stereoED_c*group_cond + (stereoED_c|sub_id),
               data = model2ED_data)

summary(model2ED)
```

Stereotyping for the target does not interact with group like projection did.

## Using ED + BFI

```{r model 2 EDBFI results}
model2EDBFI <- lmer(Targ ~ stereo_c*group_cond + (stereo_c|sub_id),
               data = EDBFI_data)

summary(model2EDBFI)
```

When combined, group still does interact with EDBFI to demonstrate stereotyping of the target.

### Plot: ME target group

```{r model 2 EDBFI plot prep}
describe(EDBFI_data$stereo_c)

mod2EDBFI_plotdata <- effect(term = "stereo_c:group_cond", 
                           xlevels = list(group_cond = c("In-group", 
                                                         "Out-group"),
                                          stereo_c = c(-1.18, 0, 1.18)), 
                           mod = model2EDBFI)

mod2EDBFI_plotdata <- as.data.frame(mod2EDBFI_plotdata)
```

```{r model 2 plot EDBFI}
ggplot(mod2EDBFI_plotdata, aes(stereo_c, fit, group = group_cond)) +
  geom_smooth(method = "lm", 
              se = FALSE, 
              size = .7, 
              colour = "black", 
              aes(linetype = group_cond)) +
  theme_minimal() +
  labs(title = "Plot from Model 2: Effect of target group on stereotyping",
       subtitle = "Higher correspondence between BFI + ED ratings indicates more stereotyping",
       y = "BFI + ED ratings for target",
       x = "BFI + ED ratings for stereotypical group member") +
   theme(legend.title = element_blank())

```

Same as just the BFI plot, people stereotype their in-group more than their out-group. However, the slope for out-group stereotyping is steeper, indicating that adding everyday likes items increases out-group stereotyping.



# Pre-reg Mod 3: Identification as moderator

```{r model 3}
model3_data <- clean_ptcheck %>% 
  select(sub_id, BFI_number, BFI_target_group, TargBFI, selfBFI_c, group_cond, 
         opin_pol_combined, stereoBFI_c, identification_c) %>% 
  na.omit() %>% 
  unique()
```

## Confirmatory: W/o stereo for power

```{r contrast codes model 4 without stereo}
contrasts(model3_data$group_cond) <- contr.sum(2)
contrasts(model3_data$group_cond)
```

```{r model 3 results without stereo}
model3_nostereo <- lmer(TargBFI ~ selfBFI_c*group_cond*identification_c + 
                          (selfBFI_c|sub_id),
               data = model3_data)
summary(model3_nostereo)
```

### Plot: Int target group & identification on projection

```{r model 3 no stereo group by ident plot prep}
describe(model3_data$identification_c)

mod3_proj_ident_effects <- effect(term = "selfBFI_c:group_cond:identification_c", 
                           xlevels = list(group_cond = c("In-group", 
                                                         "Out-group"), 
                                         identification_c = c(-1.27, 0, 1.27)), 
                           mod = model3_nostereo)

mod3_proj_ident_effects <- as.data.frame(mod3_proj_ident_effects)

mod3_proj_ident_effects %<>% 
  mutate(Identification = as.factor(identification_c),
         Identification = dplyr::recode(Identification,
                                         `-1.27` = "Low Identification",
                                         `0` = "Average Identification",
                                         `1.27` = "High Identificaiton"))
```

```{r model 3 no stereo group by ident plot}
ggplot(mod3_proj_ident_effects, aes(selfBFI_c, 
                                     fit, 
                                     group = group_cond,
                                     colour = group_cond)) +
  geom_smooth(method = "lm", se = FALSE, size = .7, colour = "black",
              aes(linetype = group_cond)) +
  facet_grid(cols = vars(Identification)) +
  theme_minimal() +
  theme(legend.title = element_blank()) +
  labs(title = "Pre-reg Model 3: Projection by identification and group membership",
       subtitle = "Stereotyping removed for power",
       x = "Personality traits for self",
       y = "Personality traits for target")
```

Counter projection becomes more severe towards the out-group as in-group identification increases.

## Exploratory: W/ stereo in model

```{r model 3 results w stereo}
model3_stereo <- lmer(TargBFI ~ selfBFI_c*group_cond*stereoBFI_c*identification_c + (selfBFI_c|sub_id),
               data = model3_data)
summary(model3_stereo)
```

The interaction with in-group identification plotted above is no longer significant when stereotyping is included as a moderator in the model. I've plotted the significant main effects and interactions below.

### Plot: ME target group on projection

```{r model 3 prep main effect group}
mod3_proj_group_stereo <- effect(term = "selfBFI_c:group_cond", 
                           xlevels = list(group_cond = c("In-group", "Out-group")), 
                           mod = model3_stereo)

mod3_proj_group_stereo <- as.data.frame(mod3_proj_group_stereo)
```

```{r Model 3 main effect group plot}
ggplot(mod3_proj_group_stereo, aes(selfBFI_c, fit, group = group_cond)) +
  geom_smooth(method = "lm", 
              se = FALSE, 
              size = .7, 
              colour = "black", 
              aes(linetype = group_cond)) +
  theme_minimal(base_size = 13) +
  theme(legend.key.size = unit(1, "cm"),
        legend.title = element_blank()) +
  labs(title = "Exp Model 3: Main effect of target group on projection",
       subtitle = "Including stereotyping as an exploratory moderator",
         x = "Personality responses for self",
         y = "Personality responses for target")
```

Same as in Model 3 - in-group identification did not impact how stereotyping removed counter projection from the main effect of target group.

### Plot: Group * stereo on projection

```{r model 4 interaction with stereo prep}
describe(model4_data$stereoBFI_c)

mod4_proj_stereo_effects <- effect(term = "selfBFI_c:group_cond:stereoBFI_c", 
                           xlevels = list(group_cond = c("In-group", "Out-group"), 
                                         stereoBFI_c = c(-1.22, 0, 1.22)), 
                           mod = model4)

mod4_proj_stereo_effects <- as.data.frame(mod4_proj_stereo_effects)

mod4_proj_stereo_effects %<>% 
  mutate(Stereotyping = as.factor(stereoBFI_c),
         Stereotyping = dplyr::recode(Stereotyping,
                                      `-1.22` = 
                                        "Low stereotyping \n (1 SD below)",
                                      `0` = 
                                        "Average stereotyping",
                                      `1.22` = 
                                        "High stereotyping  \n(1 SD above)"))
```

```{r model 4 interaction plot with stereo}
ggplot(mod4_proj_stereo_effects, aes(selfBFI_c, 
                                     fit, 
                                     group = group_cond,
                                     colour = group_cond)) +
  geom_smooth(method = "lm", se = FALSE, size = .7, colour = "black",
              aes(linetype = group_cond)) +
  facet_grid(cols = vars(Stereotyping)) +
  theme_minimal() +
  theme(legend.title = element_blank()) +
  labs(title = "Plot Model 4 with stereotyping: Projection predicted by stereotyping and group membership",
       subtitle = "Model included in-group identification as moderator",
       x = "Personality traits for self",
       y = "Personality responses for target")
```

Did not change from previous model.

### Plot: ME Identification on stereotyping

```{r model 4 stereo * ident int prep}
describe(model4_data$identification_c)

mod4_stereo_ident_effects <- effect(term = "stereoBFI_c:identification_c", 
                           xlevels = list(identification_c = c(-1.27, 0, 1.27)), 
                           mod = model4)

mod4_stereo_ident_effects <- as.data.frame(mod4_stereo_ident_effects)

mod4_stereo_ident_effects %<>% 
  mutate(Identification = as.factor(identification_c),
         Identification = dplyr::recode(Identification,
                                         `-1.27` = "Low Identification",
                                         `0` = "Average Identification",
                                         `1.27` = "High Identificaiton")) 
```

```{r}
ggplot(mod4_stereo_ident_effects, aes(stereoBFI_c, fit, group = Identification)) +
  geom_smooth(method = "lm", se = FALSE, size = .7, colour = "black",
              aes(linetype = Identification)) +
  theme_minimal() +
  labs(title = "Plot Model 4 with stereotyping: Stereotyping of target predicted by identification",
       subtitle = "Higher correspondence between BFI ratings indicates more stereotyping",
       y = "BFI ratings for target",
       x = "BFI ratings for stereotypical group member")
```

### Using ED

```{r model 4 ED with stereo data}
model4EDstereo_data <- clean_ptcheck %>% 
  select(sub_id, ED_number, TargED, stereoED_c, selfED_c, 
         group_cond, opin_pol_combined, identification_c) %>% 
  na.omit() %>% 
  unique()
```

```{r model 4 ED with stereo results, warning = FALSE, message = FALSE, error = FALSE}
model4EDstereo <- lmer(TargED ~ stereoED_c*group_cond*selfED_c*identification_c + (selfED_c|sub_id),
               data = model4EDstereo_data)

summary(model4EDstereo)
```

With identification, the ED only model did not fail to converge. Identification must have added enough unique variation to the model, which makes sense since there is a significant 4-way.

As we were interested in the interaction of identification with stereo and group on projection, I only plotted the relevant significant 4-way interaction below.

#### Plot: Projection by stereo, group, & identification

```{r model 4 ED stereo * ident *proj int prep}
describe(model4EDstereo_data$identification_c)
describe(model4EDstereo_data$stereoED_c)

mod4ED_stereo4way_effects <- effect(term = "stereoED_c:group_cond:selfED_c:identification_c", 
                           xlevels = list(identification_c = c(-1.27, 0, 1.27),
                                          stereoED_c = c(-1.02, 0, 1.02)), 
                           mod = model4EDstereo)

mod4ED_stereo4way_effects <- as.data.frame(mod4ED_stereo4way_effects)

mod4ED_stereo4way_effects %<>% 
  mutate(Identification = as.factor(identification_c),
         Stereotyping = as.factor(stereoED_c),
         Identification = dplyr::recode(Identification,
                                         `-1.27` = "Low Identification",
                                         `0` = "Ave Identification",
                                         `1.27` = "High Identificaiton"),
         Stereotyping = dplyr::recode(Stereotyping,
                                      `-1.02` = "Low stereotyping",
                                      `0` = "Ave stereotyping",
                                      `1.02` = "High stereotyping")) 
```

```{r model 4 ED stereo x ident x proj int plot}
ggplot(mod4ED_stereo4way_effects, aes(selfED_c, 
                                      fit, 
                                      group = group_cond, 
                                      colour = group_cond)) +
  geom_smooth(method = "lm", se = FALSE, size = .7, colour = "black",
              aes(linetype = group_cond)) +
  facet_wrap(vars(Identification, Stereotyping)) +
  theme_sjplot() +
  theme(legend.key.size = unit(1, "cm"),
        legend.title = element_blank()) +
  labs(title = "Projection by stereotyping, identification, and group",
       subtitle = "Projection using 'Everyday Likes' (ED) items",
       x = "ED items for self",
       y = "ED items for target")
```

Out-group counter projection is persistent with everyday likes items. However, it appears that people are also counter projecting or not projecting with their in-group, depending on identification and stereotyping. 

Specifically, low in-group identifiers who apply less stereotypes to their group, counter project with their in-group. However, as stereotype use with the in-group inceases, low identifiers go to a flat-line (ave stereotyping) and to positive projection when they are using a high amount of stereotyping with the in-group target. Average identifiers retain a relatively flat line of in-group projection, but the intercept increases as stereotype use increases. Interestingly, high in-group identifiers who employ low stereotype use positively project with their in-group, while high stereotype users show a slight negative slope (but a higher intercept). Thus, it appears that the pattern for in-group projection is opposite for low and high in-group identifiers depending on stereotype use for projection with everyday likes items. Moreover, though stereotyping does moderate the relationship of in-group projection with everyday likes items, it does not appear to impact out-group projection.

